\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections changing into pdf reviewing the text

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}%
\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

@@

\begin{figure}[h] 
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.png}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.png}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.png}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

@@

\begin{figure}[h] 
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.pdf}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.pdf}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.pdf}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.pdf}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.pdf}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}
